### 2020-06-11 report/sections/server/extensions/async.tex
Report: minor fixes to section 6.1

if (this.handler instanceof Promise)
	this.handler.then(thunk);
else
	thunk(this.handler);
\end{lstlisting}
\caption{New \texttt{performSend()} for Optional \texttt{Promise}s}
\label{subfig:newthunk}
\end{subfigure}
\caption{Adapting Send Operations in \fancyname{NodeMPST}
using a Thunk}
\label{fig:thunk}
\end{figure}

@@

\begin{figure}[!h]
\begin{lstlisting}[language=javascript,tabsize=2]
(*@\hl{let used = false;}@*)
...
return class extends React.Component {
	render() {
		const props = {
			[eventLabel as string]: (event) => {
				(*@\hl{if (used) return;}@*)
				(*@\hl{used = true;}@*)

				const result = handler(event);
				if (result instanceof Promise)
					result.then(send);
				else
					send(result);
			}		
		}
	}
}
\end{lstlisting}
\captionof{lstlisting}{\dots}
\label{lst:asynclinearcheck}
\end{figure}

>>>>

if (this.handler instanceof Promise) {
	this.handler.then(thunk);
} else {
	thunk(this.handler);
}
\end{lstlisting}
\caption{New \texttt{performSend()} for Optional \texttt{Promise}s}
\label{subfig:newthunk}
\end{subfigure}
\caption{Adapting Send Operations in \fancyname{NodeMPST}
using a Thunk}
\label{fig:thunk}
\end{figure}

@@

\begin{figure}[!h]
\begin{lstlisting}[language=javascript]
(*@\hl{let used = false;}@*)
...
return class extends React.Component {
	render() {
		const props = {
			[eventLabel as string]: (event) => {
				(*@\hl{if (used) return;}@*)
				(*@\hl{used = true;}@*)

				const result = handler(event);
				if (result instanceof Promise) {
					result.then(send);
				} else {
					send(result);
				}
			}		
		}
	}
}
\end{lstlisting}
\captionof{lstlisting}{Generating Runtime Linearity Checks for
React Send State Components}
\label{lst:asynclinearcheck}
\end{figure}
